A full approximation scheme multilevel method \\ for nonlinear variational inequalities

### 2023-07-14 paper/fascd.tex
Small edits and a comment

\begin{abstract}
We present the \emph{full approximation scheme constraint decomposition} (FAScd) multilevel method for solving variational inequalities (VIs).  FAScd is a common extension of the full approximation scheme (FAS) multigrid technique for nonlinear partial differential equations, due to A.~Brandt, and the constraint decomposition (CD) method introduced by X.-C.~Tai for VIs arising in optimization.  We extend the CD idea by exploiting the telescoping nature of certain function space subset decompositions arising from multilevel mesh hierarchies.  Then, by applying strong smoothers, with work proportional to the number of unknowns on a finite element mesh level, we demonstrate that FAScd V-cycles exhibit excellent mesh-independent convergence rates and that FAScd F-cycles (full multigrid) are optimal solvers.  The example problems include unilateral and bi-obstacle VI problems, with differential operators which are symmetric linear, nonsymmetric linear, and nonlinear.  Our examples demonstrate very good convergence even on problems where other multilevel VI solvers struggle.
\end{abstract}

@@

% to regenerate from git@bitbucket.org:pefarrell/fascd.git: examples/:
%   $ mpiexec -n 16 --map-by core --bind-to hwthread python3 sia.py -levs 8 -bumps \
%       -mcoarse 8 -fascd_cycle_type full -fascd_monitor -fascd_rtol 2.0e-4 \
%       -fascd_atol 1.0e-8 -o sialev8.pvd
\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.95\textwidth]{fixfigs/sialev8scene.png}
\end{center}
\caption{Solution of Example \ref{ex:sia} over a bumpy bedrock topography, with the ice speed as surface coloring, and 100-times vertical exageration.}
\label{fig:results:siascene}
\end{figure}

>>>>

\begin{abstract}
We present the \emph{full approximation scheme constraint decomposition} (FAScd) multilevel method for solving variational inequalities (VIs).  FAScd is a common extension of the full approximation scheme (FAS) multigrid technique for nonlinear partial differential equations, due to A.~Brandt, and the constraint decomposition (CD) method introduced by X.-C.~Tai for VIs arising in optimization.  We extend the CD idea by exploiting the telescoping nature of certain function space subset decompositions arising from multilevel mesh hierarchies.  Then, by applying strong smoothers, with work proportional to the number of unknowns on a given mesh level, we demonstrate that FAScd V-cycles exhibit excellent mesh-independent convergence rates and that FAScd F-cycles (full multigrid) are optimal solvers.  The example problems include unilateral and bilateral VI problems, with differential operators which are symmetric linear, nonsymmetric linear, and nonlinear.  Our examples demonstrate very good convergence even on problems where other multilevel VI solvers struggle.
\end{abstract}

@@

% to regenerate from git@bitbucket.org:pefarrell/fascd.git: examples/:
%   $ mpiexec -n 16 --map-by core --bind-to hwthread python3 sia.py -levs 8 -bumps \
%       -mcoarse 8 -fascd_cycle_type full -fascd_monitor -fascd_rtol 2.0e-4 \
%       -fascd_atol 1.0e-8 -o sialev8.pvd
\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.95\textwidth]{fixfigs/sialev8scene.png}
\end{center}
\caption{Solution of Example \ref{ex:sia} over a bumpy bedrock topography, with the ice speed as surface coloring, and 100-times vertical exageration.}
\label{fig:results:siascene}
\end{figure}
\pef{Could we make the bedrock grey?}
